Bow shocks, bow waves, and dust waves. IV. Bow shape statistics

### 2019-04-29 papers/Papers1234/sec-quadrics-observations.tex
Finish description of LL arcs shape statistics

\begin{figure*}
  \centering
  \setlength\tabcolsep{0pt}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.5\textwidth]
    {figs/mipsgal-Rc-R90-zoom-annotated}
        & \includegraphics[width=0.5\textwidth]
          {figs/mipsgal-Rc-R90-thumbnails} 
  \end{tabular}
  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
    of dimensionless radius of curvature versus perpendicular radius.
    The regions corresponding to different classes of cuadrics are
    shown by shading (see \S~\ref{sec:conic}): oblate spheroids (light
    gray background); prolate spheroids (darker gray background);
    paraboloids (curved black line); hyperboloids (white background).
    (a) Individual sources with bow shock fit quality rating of 3-star
    or above.  All 5-star sources plus those 4-star sources with
    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a}
    catalog number.  Horizontal error bars do not directly reflect the
    uncertainty in \(\Pi\) but are instead simply the standard
    deviation from the circle fit of bowshock points \(R_k\) within
    \(\pm 45\degr\) of the axis.  Values on the vertical axis
    represent the average of \(\Lambda_{+}\) and \(\Lambda_{-}\), with thin
    vertical error bars showing the difference between \(\Lambda_{+}\) and
    \(\Lambda_{-}\), and thick vertical error bars showing the rms
    dispersion of \(R_k\) about these values for bow shock points
    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
    directions.  (b) Kernel density estimator (KDE) of the
    distribution for 3-star sources (blue, filled contours) and 4-
    plus 5-star sources (orange/brown, unfilled contours).  The KDE
    uses an anisotropic gaussian kernel with bandwidths of
    \(0.18 \times 0.12\). Thumbnail images of representative 4- and 5-star
    sources at different points on the \(\Pi\)--\(\Lambda\) plane are
    also shown. The angular scale of each image is indicated by a
    yellow circle of diameter \(7.5''\), centered on the stellar
    source.}
  \label{fig:mipsgal-shapes}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Shape comparison between Orion Nebula arcs and OB star
    bow shocks.  Other details of the plots are as in
    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
    except that the diagnostic plots are zoomed out to encompass
    larger ratio values, and a larger KDE smoothing bandwidth of
    \(0.3 \times 0.2\) is used.}
  \label{fig:ll-compare-mipsgal}
\end{figure}

@@

>>>>

\begin{figure*}
  \centering
  \setlength\tabcolsep{0pt}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[width=0.5\textwidth]
    {figs/mipsgal-Rc-R90-zoom-annotated}
        & \includegraphics[width=0.5\textwidth]
          {figs/mipsgal-Rc-R90-thumbnails} 
  \end{tabular}
  \caption[]{MIPSGAL sources on the bow shock shape diagnostic diagram
    of dimensionless radius of curvature versus perpendicular radius.
    The regions corresponding to different classes of cuadrics are
    shown by shading (see \S~\ref{sec:conic}): oblate spheroids (light
    gray background); prolate spheroids (darker gray background);
    paraboloids (curved black line); hyperboloids (white background).
    (a) Individual sources with bow shock fit quality rating of 3-star
    or above.  All 5-star sources plus those 4-star sources with
    \(\Pi < 1\) are labelled with their \cite{Kobulnicky:2016a} catalog
    number.  Horizontal error bars do not directly reflect the
    uncertainty in \(\Pi\) but are instead simply the standard deviation
    from the circle fit of bowshock points \(R_k\) within
    \(\pm 45\degr\) of the axis.  Values on the vertical axis
    represent the average of \(\Lambda_{+}\) and \(\Lambda_{-}\), with thin
    vertical error bars showing the difference between \(\Lambda_{+}\) and
    \(\Lambda_{-}\), and thick vertical error bars showing the rms
    dispersion of \(R_k\) about these values for bow shock points
    within \(\pm 10\degr\) of the \(+90\degr\) and \(-90\degr\)
    directions.  (b) Kernel density estimator (KDE) of the
    distribution for 3-star sources (blue, filled contours) and 4-
    plus 5-star sources (orange/brown, unfilled contours).  The KDE
    uses an anisotropic gaussian kernel with bandwidths of
    \(0.06 \times 0.04\) in \(\log_{10}\) units. Thumbnail images of
    representative 4- and 5-star sources at different points on the
    \(\Pi\)--\(\Lambda\) plane are also shown. The angular scale of each image
    is indicated by a yellow circle of diameter \(7.5''\), centered on
    the stellar source.}
  \label{fig:mipsgal-shapes}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Shape comparison between Orion Nebula arcs and OB star
    bow shocks.  Other details of the plots are as in
    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
    except that a larger KDE smoothing bandwidth of
    \(0.06 \times 0.045\) is used for the Orion Nebula sample.}
  \label{fig:ll-compare-mipsgal}
\end{figure}

@@

The resultant shape distribution for the Orion Nebula arcs is shown in
Figure~\ref{fig:ll-compare-mipsgal}, where it is compared with the OB
star shapes from \S~\ref{sec:ob-shapes}.  It can be seen that both the
planitude and alatude distributions are shifted towards higher values,
with median values of \(\Pi = 2.70\) and \(\Lambda = 2.55\).  The difference
from the MIPSGAL sources (\(\Pi = 1.57\) and \(\Lambda = 1.69\)) is highly
statistically significant, as indicated by extremely low \(p\)-values
for the Anderson--Darling tests.  It is also at least 4 times larger
than the systematic fitting uncertainties discussed in the previous
paragraph.  On closer inspection, it appears that the shape
distribution is bimodal.  Four of the sources (005--514, 4468--605,
116--3101, 308--3036) are similar to typical OB stars, with
\(\Lambda \approx \Pi \approx 1.5\), whereas the remainder are concentrated in the range
\(\Pi = 2\) to \(4\), with an extended tail towards higher planitude.
The alatudes mainly follow the line for parabolas,
\(\Lambda = (2\Pi)^{1/2}\) (see App.~C of Paper~0), and the deviations from
this line can be readily understood in terms of peculiar morphologies
of the source (Fig.~\ref{fig:ll-arcs}).  For instance, LL~4 and
266--558 both show large alatudes for their respective planitudes and
these are both sources where the bow shock wings seem to bend outwards
instead of following the curve from the apex region.  In contrast,
030--524 has a small alatude for its planitude and this is a very
asymmetric source with an apparent corner to the shell on one side.
